{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-01 bmvc_review.tex
Comments Answered - Figures Updated - Conclusion Checked

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications for embedded systems. This is primarily because most of
the embedded systems already includes image acquisition pipeline and a
tremendous amount of progresses on research has been made for many
areas in computer vision. However, to successfully deploy a computer
vision algorithm on any existing embedded systems, a vision algorithm
needs to satisfy some criteria: minimal, manual intervention after
deployment and small footprint of computing resource consumption and
on executable code, with the assumption of reasonably good
performance. To this end, in this paper, we propose an ensemble of the
kernelized correlation filters (KCF), we call {\it E}nKCF, for a
single-target object tracking. In particular, we developed a committee
of KCFs to specifically address the scale-change and dynamic maneuver
of the target over frames. In addition, we devised a Bayes filter for
a smooth transition between individual KCFs' executions. To minimize
the effect of drifting, we also developed another algorithm that
detects target-lost, uses an existing object proposal method (e.g.,
``Edge Box'') to re-detect the lost target, and re-initializes the
previous tracking for a long-term tracking. To verify the usefulness
of the proposed method, we compared the performance of ours to those
of the existing online tracking methods. Experimental results showed
that the performance of ours are 72.53\% for precision on 20 pixels
and 52.90\% for success rate for OTB100 data, and 55.71\% and 41.71\%
for UAV123 data. These results confirmed that our method outperformed
the existing ones over 5\% on precision on 20 pixels and 10-20\% on
AUC on average. Our implementation ran at 340 fps for OTB100 and at
416 fps for UAV123 data that is faster than DCF (292 fps) for OTB100
and KCF (292 fps), DCF (457 fps), and STC (350 fps) for UAV123.
\end{abstract}

@@

In this paper, we propose a single-target tracking aiming at running
on any embedded or mobile platforms that doesn't require an offline
training, and can run on an embedded system. In particular, we would
like to make our algorithm 1) learn the appearance model of a target
on the fly and 2) run as fast on a typical desktop as up to 300Hz so
that it could run, at least, faster than 30Hz when it is deployed on a
low-end, embedded system. With these features, our tracking algorithm
is ready to track an object of interest when it is deployed on an
embedded system. To this end, an online object tracking is more
appropriate.

One of the dominant frameworks for online object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that the target location is given at the very first
image frame like other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a circulant matrix
\cite{henriques2015high}. One can optimally solve this regression
problem using a ridge regression in a closed form. However, such a
solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequecny domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can be easily implemented and run very efficiently
in an online fashion. In fact, a variant of the correlation filter,
the kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object trackin results and
outperformed other state-of-the-art tracking algorithms, for example,
in VOT15 challenge, in terms of run-time and tracking
accuracy. However, the vanilla form of such an online tracker is prone
to drift, and fails to track a target over a long period of time
primarily \cite{henriques2015high} because of the dilemma of
stability-plasticity in updating appearance model, where the
appearance model will be overfitted to only the images used to train
and a compromise on the frequency of updating the model is carefully
implemented \cite{santner2010prost}. For example, a naive way of
handling a scale change of a target could reduce the run-time
performance from 300 to 100 fps. A seemingly obvious way of addressing
the scale change is to scan the region of interest (ROI) with
templates in different dimensions based on pre-defined scale ratios to
find the target
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. Due
to the computational nature of correlation filter, however, this
approach would merely increase the computational complexity because it
has to run the correlation filter multiple times on each frame.

Another way of handling the scale change for the correlation filter
based approach is to find a correct scale at a location where a target
highly likely appears \cite{zhang2014fast}. In particular, they uses
the MOSSE tracker to estimate a target's translation. The scale is
updated in a way where the confidence map is used to determine the
scale change between successive frames. This is because they assumes
the scale of a target wouldn't change much over two consecutive
frames. Similarly \cite{ma2015long} used two KCFs to learn the
translation and scale of a target separately. To more specific, a KCF
is used to learn the translation of the target and its
background. Given this, another KCF is used to learn the target area
to estimate a new scale of the target. However, because of running
more than a KCF on each frame, this method degrades its run-time
performance (i.e., $\leq 50 fps$). Our method is motivated by this
idea -- the idea of deploying multiple KCFs to address the issues of
single target tracking: scale and translation. In this paper, we use
an ensemble of KCFs in turn, instead of running them all together on
every frame. By doing so, we could still address the scale change and
estimate target's motion efficiently while increasing run-time
performance. In particular, we deploy three KCF in turn:
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). Figure \ref{fig:Filters} shows examples of the ROIs
associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.
\begin{comment}
{\it We may not need this.}
The recent progress on development of convolutional neural networks
(CNN) is astonishing as since the AlexNet \cite{krizhevsky12} broke
the record for the ImageNet competition, at every year, new and better
results are reported. Moreover, there have been many attempts to
deploy CNN on the mobile devices
\cite{wu2016quantized,giusti2015}. But the inherent limitation of such
a supervised learning based object tracking is that an either online
\cite{nam2016} or offline \cite{held2016} training tracker has to be
prior to deploy the algorithm.
\end{comment}

The contributions of this study are as follows.
\begin{itemize}
\item \textbf{Novel Single-Target Tracking in a Very High-Speed ($\geq300$ fps) } Our
  algorithm, {\it E}nKCF, deploys an ensemble of KCF in turn to more
  efficiently address the scale variance and the dynamic maneuver of a
  target while perserving run-time performance as high as possible. To
  minimize any potential performance gap from transiting one KCF to
  another, we use a Bayes filter. The workflow of the  {\it E}nKCF can
  be visualized in fig.~\ref{Workflow_figure_EnKCF}. The proposed tracker is tested on UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}} and OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
  datasets.

\item \textbf{Slight Modification of the proposed EnKCF for Handling Large Motion} Our second algorithm, 
{\it E}nKCF2 leverages the flexibility of the ensemble of KCFs approach we propose. The original {\it E}nKCF is slighlty modified to track fast motions and handle large ego-motion. We do not integrate the particle filter in {\it E}nKCF2 as we test it on a temporally downsampled UAV123 dataset (UAV123$\_$10fps) including sequences with large ego-motion on the low frame rate UAV platform. Particle Filter can be deployed in case the camera motion is known. The proposed framework can be seen in fig.~\ref{Workflow_figure_EnKCF2}.

@@

In this paper, we extends the KCF in that multiple KCFs are deployed,
in turn, to address a target's scale change and dynamic maneuvers
while preserving the overall execution time very fast, i.e., $\ge$ 300
fps. The efficient nature of KCF computation results in a
small-footprint, executable. Such a fast execution will facilitate to
deploy the proposed algorithm on any embedded systems.

@@

After Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high}, many variation of KCF were
investigated. In particular, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is particularly similar to that of
\cite{ma2015long} in that more than one KCF is used to address the
challenges of single target tracking. But ours is different from that
of \cite{ma2015long} in that we do not use those three KCFs together
at every frame, but alternatively at every three frame. The way our
algorithm is alternating multiple KCFs in different goals intuitively
makes sense in that the appearance of consecutive images does not
change much. Although it varies based on the scene, learning a
correlation filter a frame would not be much different from the one
learned using the image few or $k$ frames later. By alternating three
KCFs in turn, our algorithm runs as fast as or faster than the
original KCF. From our experiments, we empirically found that five is
the optimal for $k$ in terms of precision and success rates. We'll
detail this at the experimental section later.

@@

The order of running these three KCFs is important as each of these
filters aims at addressing different chanllenges while perserving
run-time performance as fast as possible. The \textit{target+large
  background} translation filter, $R_{t}^{L}$, is intended to run
right after the scale filter, $R_s$, runs which is applied at every
$k=5$ frames. We run these two filters this way because we want to
minimize any drifts that are likely to happen running only $R_{s}$. In
addition, the filter, $R_{t}^{S}$, is applied to every other frames
before $R_{S}$ and right after two consecutive frames running
$R_{t}^{L}$. By doing so, we can integrate more discriminative shape
features that can not be fully learned by $R_{t}^{L}$ as it contains
contribution of large background in the learned model. The filter,
$R_{t}^{L}$ uses shape and color information together to recover from
any potential drifts -- drifts could happen only looking the target's
scale by the filter, $R_{s}$.

{\it Burak: Rewrite the following paragraph.}

In summary, the filter, $R_{t}^{S}$, will handle the absence of scale
adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$
focuses on addressing the absence of translation estimation module in
$R_{S}$ and $R_{t}^{S}$ addresses the weakness of $R_{t}^{L}$ that it
can not learn very useful shape features
alone.

Figure \ref{Workflow_figure_EnKCF} illustrates the workflow of the
proposed algorithm and Figure \ref{alg:MKCF} shows the pseudo-code of
{\it E}nKCF.

\begin{algorithm}
	\caption{The {\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
	\begin{algorithmic}[1]
	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
	\State \textbf{Output} : 
				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
						\State Estimated Target State $x_{t} = (x_{t-1},y_{t-1},s_{t})$,
						Scale filter (\textit{target-only}) model $R_{s}$.
			     \EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
						Large Area Translation Filter model $R_{t}^{L}$.
				\EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Small Area Translation Filter model $R_{t}^{S}$.
				\EndIf
	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
				\State // Translation Estimation
				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
				\State // Translation Estimation
				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
				\State Skip translation estimation for $R_{s}$ (Condition 1);
				\State // Scale Estimation
			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
		         \State Skip it for $R_{t}^{L}$ (Condition 1),
				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
				\State // Update Translation
				\State Perform Importance Re-sampling for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
			    \State // Model Update
				\If{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}
				\State Update $R_{s}$ (Condition 1);
				\EndIf							 
				\If{$PSR(y_{R_{t}^{L}}) \geq T_{R_{t}^{L}}$} 
				\State Update $R_{t}^{L}$ (Condition 2);
				\EndIf	
			     \If{$PSR(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
				\State Update $R_{t}^{S}$ (Condition 3);
			     \EndIf		
	\EndProcedure	
	\end{algorithmic}
\end{algorithm}

@@

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter tracker has recently been
increasingly popular due to its operation at hundreds of frames per
second with state-of-the-art tracking capabilities even in challenging
cases such as VOT15 dataset. Its computational efficiency arises from
its use of the discrete fourier transform of the circulant matrix and
frequency domain element-wise operations known as hadamard product and
division. The first example of frequency domain trackers is the Linear
Correlation Filter tracker known as MOSSE tracker. It minimizes the
ridge regression function in the frequency domain using a single
template with continous desired gaussian response. The KCF tracker, on
the other hand, minimizes the regularized ridge regression function
shown below.
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The $c$ parameter included in
\cite{henriques2015high,galoogahi2013multi} makes it possible to
integrate multi-channel features such as HoG and colour into the ridge
regression function. The closed-form solution for the
eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the
derivative of $E$ w.r.t $w$ to $0$. The solution in the primal domain
can be formulated as
\begin{equation}
w = (X^{T}X+\lambda)^{-1}y
\label{eq:SpatialSolution}
\end{equation}
where $X$ and $\lambda$ represent the training samples and
regularization term. The same cost function in the Fourier domain can
be represented as
\begin{equation}
w = (X^{H}X+\lambda I)^{-1}X^{T}y
\label{eq:FourierSolution}
\end{equation}
More information on the spatial and fourier domain solutions can be
found in \cite{henriques2015high}. The MOSSE tracker does not make use
of $\lambda$ and only one training sample with desired response is
used to update $w$. This framework does not include enough background
information into the training framework with a single template. The
application of the circulant matrix theorem into the
eq.~\ref{eq:Closedform_RidgeReg} makes it possible to include many
background patches at a similar computational complexity. A circulant
matrix includes the circularly shifted patches of the positive
training sample $x$ by a cylic shift operator.

@@

\subsection{Particle Filter} \label{sc:PF}
The proposed {\it E}nKCF algorithm can cause undesired drift and noise
in tracking due to independent and less frequent application of the
correlation filters.

{\it Burak: When we explain EnKCF, we've already used potential drifts
  are the reason why we want to have three KCFs. If we're talking
  about the same, kind of drifts, you have to be more careful. Having
  this section about particle filter will make it impractical or
  usefulness to have three KCFs.}

To mitigate the drift effect further and reduce the noise, a Bayes
Filter representing the evolution of target's motion can be added into
our {\it E}nKCF tracking framework. To achieve this, we consider a
variant of a Bayes Filter, \textit{Particle Filter}. The Particle
Filter is a Sequential Monte Carlo method that uses a number of sample
points to represent the posterior probability density functions (pdf)
of the target motion.  The approximation becomes optimal with the
infinite number of particles, however, its run-time complexity grows
exponentially with the number of elements in the state space matrix,
$X_{t}$. As the focus of this study is to design a high speed tracker,
we keep the number of state space elements low and implement
computationally efficient \textit{Weight Function} and
\textit{Importance-Resampling} modules. We represent the state space
matrix as $X_{t} = \lbrace x,y,V_{x},V_{y}\rbrace$ where $x$ and $y$
are the centroid of the target and $V$ represents the velocity
components. We transit the particles with the first order Constant
Velocity model. The centroid components are applied Gaussian Noise
whereas the velocity components are assigned uniform noise
representative of most of the objects in our tests. The observation
likelihood is formulated based on the confidence map of $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$.  The weights for the particles are computed
as
\begin{equation}
	w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)
\end{equation}
where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and
$N$ denotes the size of the window in consideration. We can also use
the spatial distance of particles to the peak of the confidence map,
however, we believe that this approach could result in further drifts
in the case of multi-modal distributions.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications for embedded systems. This is primarily because most of
the embedded systems already includes image acquisition pipeline and a
tremendous amount of progresses on research has been made for many
areas in computer vision. However, to successfully deploy a computer
vision algorithm on any existing embedded systems, a vision algorithm
needs to satisfy some criteria: minimal, manual intervention after
deployment and small footprint of computing resource consumption and
on executable code, with the assumption of reasonably good
performance. To this end, in this paper, we propose an ensemble of the
kernelized correlation filters (KCF), we call {\it E}nKCF, for a
single-target object tracking. In particular, we developed a committee
of KCFs to specifically address the scale-change and dynamic maneuver
of the target over frames. In addition, we devised a Bayes filter for
a smooth transition between individual KCFs' executions. Also, we slightly
modify the {\it E}nKCF to perform tracking in low frame rate videos dominated by large ego-motion.
large ego-motion.To verify the usefulness of the proposed method, we compared the performance of ours to those
of the existing online tracking methods. Experimental results showed
that the performance of ours are 72.53\% for precision on 20 pixels
and 52.90\% for success rate for OTB100 data, and 55.71\% and 41.71\%
for UAV123 data. These results confirmed that our method outperformed
the existing ones over 5\% on precision on 20 pixels and 10-20\% on
AUC on average. Our implementation ran at 340 fps for OTB100 and at
416 fps for UAV123 data that is faster than DCF (292 fps) for OTB100
and KCF (292 fps), DCF (457 fps), and STC (350 fps) for UAV123.
\end{abstract}

@@

In this paper, we propose a single-target tracking aiming at running
on any embedded or mobile platforms that doesn't require an offline
training, and can run on an embedded system. In particular, we would
like to make our algorithm 1) learn the appearance model of a target
on the fly and 2) run as fast on a typical desktop as up to $300$-$400$Hz so
that it could run, at least, faster than 30Hz when it is deployed on a
low-end, embedded system. With these features, our tracking algorithm
is ready to track an object of interest when it is deployed on an
embedded system. To this end, an online learning highly efficient object tracking is more
appropriate.

One of the dominant frameworks for online object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that the target location is given at the very first
image frame like other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a circulant matrix
\cite{henriques2015high}. One can optimally solve this regression
problem using a ridge regression in a closed form. However, such a
solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can be easily implemented and run very efficiently
in an online fashion. In fact, a variant of the correlation filter,
the kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object tracking results and
outperformed other state-of-the-art tracking algorithms, for example,
in VOT15 challenge, in terms of run-time and tracking
accuracy. However, the vanilla form of such an online tracker is prone
to drift, and fails to track a target over a long period of time
primarily \cite{henriques2015high} because of the dilemma of
stability-plasticity in updating appearance model, where the
appearance model will be overfitted to only the images used to train
and a compromise on the frequency of updating the model is carefully
implemented \cite{santner2010prost}. For example, a naive way of
handling a scale change of a target could reduce the run-time
performance from 300 to 100 fps. A seemingly obvious way of addressing
the scale change is to scan the region of interest (ROI) with
templates in different dimensions based on pre-defined scale ratios to
find the target
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. Due
to the computational nature of correlation filter, however, this
approach would merely increase the computational complexity because it
has to run the correlation filter multiple times on each frame.

Another way of handling the scale change for the correlation filter
based approach is to find a correct scale at a location where a target
highly likely appears \cite{zhang2014fast}. In particular, they use
the MOSSE tracker to estimate a target's translation. The scale is
updated in a way where the confidence map is used to determine the
scale change between successive frames. This is because they assume
the scale of a target wouldn't change much over two consecutive
frames. Similarly \cite{ma2015long} used two KCFs to learn the
translation and scale of a target separately. To be more specific, a KCF
is used to learn the translation of the target and its
background. Given this, another KCF is used to learn the target area
to estimate a new scale of the target. However, because of running
more than a KCF on each frame, this method degrades its run-time
performance (i.e., $\leq 50 fps$). Our method is motivated by this
idea -- the idea of deploying multiple KCFs to address the issues of
single target tracking: scale and translation in a highly efficient manner. 
In this paper, we use an ensemble of KCFs in turn, instead of running them all together on
every frame. By doing so, we could still address the scale change and
estimate target's motion efficiently while increasing run-time
performance. In particular, we deploy three KCF in turn:
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). Figure \ref{fig:Filters} shows examples of the ROIs
associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.
\begin{comment}
{\it We may not need this.}
The recent progress on development of convolutional neural networks
(CNN) is astonishing as since the AlexNet \cite{krizhevsky12} broke
the record for the ImageNet competition, at every year, new and better
results are reported. Moreover, there have been many attempts to
deploy CNN on the mobile devices
\cite{wu2016quantized,giusti2015}. But the inherent limitation of such
a supervised learning based object tracking is that an either online
\cite{nam2016} or offline \cite{held2016} training tracker has to be
prior to deploy the algorithm.
\end{comment}

The contributions of this study are as follows.
\begin{itemize}
\item \textbf{Novel Single-Target Tracking in a Very High-Speed ($\geq300$ fps) } Our
  algorithm, {\it E}nKCF, deploys an ensemble of KCF in turn to more
  efficiently address the scale variance and the dynamic maneuver of a
  target while preserving run-time performance as high as possible. To
  minimize any potential performance gap from transiting one KCF to
  another, we use a Bayes filter. The workflow of the  {\it E}nKCF can
  be visualized in fig.~\ref{Workflow_figure_EnKCF}. The proposed tracker is tested on UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}} and OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
  datasets.

\item \textbf{Slight Modification of the proposed {\it E}nKCF for Handling Large Motion} Our second algorithm, 
{\it E}nKCF2 leverages the flexibility of the ensemble of KCFs approach we propose. The original {\it E}nKCF is slighlty modified to track in low frame rate videos ($10$fps) dominated by large ego-motion. We do not integrate the particle filter in {\it E}nKCF2 as we test it on a temporally downsampled UAV123 dataset (UAV123$\_$10fps) including sequences with large ego-motion on a UAV platform. Particle Filter can be deployed in case the camera motion is known. The run-time performance decreases to $150$ fps, however, ratio of the video frame rate and run-time performance is similar to {\it E}nKCF. The proposed framework can be seen in fig.~\ref{Workflow_figure_EnKCF2}.

@@

In this paper, we extend the KCF in that multiple KCFs are deployed,
in turn, to address a target's scale change and dynamic maneuvers
while preserving the overall execution time very fast, i.e., $\ge$ 300
fps. The efficient nature of KCF computation results in a
small-footprint, executable. Such a fast execution will facilitate to
deploy the proposed algorithm on any embedded systems.

@@

After Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15\footnote{\url{http://www.votchallenge.net/vot2015/}} challenge, many variation of KCF were
investigated. In particular, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is particularly similar to that of
\cite{ma2015long} in that more than one KCF is used to address the
challenges of single target tracking. But ours is different from that
of \cite{ma2015long} in that we do not use those multiple KCFs together
at every frame, but alternatively at every three frame. The way our
algorithm is alternating multiple KCFs in different goals intuitively
makes sense in that the appearance of consecutive images does not
change drastically. Although it varies based on the scene, learning a
correlation filter a frame would not be much different from the one
learned using the image few or $k$ frames later. By alternating three
KCFs in turn, our algorithm runs as fast as or faster than the
original KCF. From our experiments, we empirically found that five is
the optimal for $k$ in terms of precision and success rates. We'll
detail this at the experimental section later.

@@

The order of running these three KCFs is important as each of these
filters aims at addressing different chanllenges while perserving
run-time performance as fast as possible. The \textit{target+large
  background} translation filter, $R_{t}^{L}$, is intended to run
right after the scale filter, $R_s$, runs which is applied at every
$k=5$ frames. We run these two filters this way because we want to
minimize any drifts that are likely to happen running only $R_{s}$. In
addition, the filter, $R_{t}^{S}$, is applied to every other frames
before $R_{S}$ and right after two consecutive frames running
$R_{t}^{L}$. By doing so, we can integrate more discriminative shape
features that can not be fully learned by $R_{t}^{L}$ as it contains
contribution of large background in the learned model. The filter,
$R_{t}^{L}$, uses shape and color information together to recover from
any potential drifts -- drifts could happen only looking the target's
scale by the filter, $R_{s}$.

In summary, the scale filter, $R_{s}$, handles the scale change providing more accurate
ROIs to $R_{t}^{L}$ and $R_{t}^{S}$. The translation filter, $R_{t}^{L}$, concentrates on a large search area to better recover from any potential drifts due to application of $R_{S}$ in previous frame. $R_{t}^{S}$, on the other hand, addresses the drawback of $R_{t}^{L}$ that it learns noisy shape features due to its large search area. Figure \ref{Workflow_figure_EnKCF} illustrates the workflow of the
proposed algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of
{\it E}nKCF. In the following section, we will briefly mention the theory behind the KCF.

\begin{algorithm}
	\caption{The {\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
	\begin{algorithmic}[1]
	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
	\State \textbf{Output} : 
				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Scale filter (\textit{target-only}) model $R_{s}$.
			     \EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
						Large Area Translation Filter model $R_{t}^{L}$.
				\EndIf
				\If{$fc\:\%\:n=3\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Small Area Translation Filter model $R_{t}^{S}$.
				\EndIf
	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
				\State // Translation Estimation
				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
				\State // Translation Estimation
				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
				\State Skip translation estimation for $R_{s}$ (Condition 1);
				\State // Scale Estimation
			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
		        \State Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ (Condition 1, and 2),
				\State // Update Translation
				\State Perform Importance Re-sampling (if necessary) for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
			    \State // Model Update
				\If{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}
				\State Update $R_{s}$ (Condition 1);
				\EndIf							 
				\If{$PSR(y_{R_{t}^{L}}) \geq T_{R_{t}^{L}}$} 
				\State Update $R_{t}^{L}$ (Condition 2);
				\EndIf	
			     \If{$PSR(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
				\State Update $R_{t}^{S}$ (Condition 3);
			     \EndIf		
	\EndProcedure	
	\end{algorithmic}
\end{algorithm}

@@

{\it YoungWoo : What do you mean by this? Should we move it up before the EnKCF introduction? or Should we include more EnKCF-related text in it? I trimmed it further. I wanted to keep some equations because they include hyper-paramaters that is important for EnKCF.}

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter tracker has recently been
increasingly popular due to its operation at hundreds of frames per
second with state-of-the-art tracking capabilities even in challenging
cases. Its computational efficiency arises from its use of the discrete fourier transform of the circulant matrix and frequency domain element-wise operations known as hadamard product and
division. The first example of frequency domain trackers is the MOSSE tracker running at $700$fps \cite{bolme2010visual}. It minimizes the ridge regression function in the frequency domain using a single
template and intensity features. The KCF tracker, on the other hand, minimizes the regularized ridge regression function shown below.
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The $c$ parameter included in
\cite{henriques2015high,galoogahi2013multi} makes it possible to
integrate multi-channel features such as HoG and colour into the ridge
regression function. The closed-form solution for the
eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the
derivative of $E$ w.r.t $w$ to $0$. The primal solution in the frequency domain is formulated
as
%\begin{equation}
%w = (X^{T}X+\lambda)^{-1}y
%\label{eq:SpatialSolution}
%\end{equation}
\begin{equation}
w = (X^{H}X+\lambda I)^{-1}X^{T}y
\label{eq:FourierSolution}
\end{equation}
where $X^{H}$ and $\lambda$represent the complex-conjugate of training samples and
regularization term. More documentation on the spatial and fourier domain solutions can be
found in \cite{henriques2015high}. The MOSSE tracker uses one training sample centred at estimated position of the target. This framework does not include enough background
information into the learned model,$w$. The
application of the circulant matrix theorem into the
eq.~\ref{eq:Closedform_RidgeReg} makes it possible to include many
background patches at a similar computational complexity. A circulant
matrix includes the circularly shifted patches of the positive
training sample $x$ by a cylic shift operator.

@@

\subsection{Particle Filter} \label{sc:PF}
The proposed {\it E}nKCF tracker does not update target's translation at every
$n=5$ frames due to application of a scale filter, $R_{s}$. To avoid this to perform 
smoother tracking, a Bayes Filter representing the evolution of target's motion can be added into our {\it E}nKCF tracking framework. To achieve this,
we consider a variant of a Bayes Filter, \textit{Particle Filter}. The Particle
Filter is a Sequential Monte Carlo method that uses a number of sample
points to represent the posterior probability density functions (pdf)
of the target motion.  The approximation becomes optimal with the
infinite number of particles, however, its run-time complexity grows
exponentially with the number of elements in the state space matrix,
$X_{t}$. As the focus of this study is to design a high speed tracker,
we keep the number of state space elements low and implement
computationally efficient \textit{Weight Function} and
\textit{Importance-Resampling} modules. We represent the state space
matrix as $X_{t} = \lbrace x,y,V_{x},V_{y}\rbrace$ where $x$ and $y$
are the centroid of the target and $V$ represents the velocity
components. We transit the particles with the first order Constant
Velocity model. The centroid components are applied Gaussian Noise
whereas the velocity components are assigned uniform noise
representative of most of the objects in our tests. The observation
likelihood is formulated based on the confidence map of $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$.  The weights for the particles are computed
as
\begin{equation}
	w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)
\end{equation}
where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and
$N$ denotes the size of the window in consideration in confidence map. We can also use
the euclidean distance of particles to the location of maximum response of 
the confidence map, however, we believe that this approach could result in drifts
in the case of multi-modal distributions.

The importance re-sampling module is triggered when the number of
effective particles is smaller than a pre-defined threshold to avoid
variance getting too small \cite{thrun2005probabilistic}. Re-sampling
is implemented with efficient low-variance ratio method
\cite{thrun2005probabilistic}. Finally, the expected mean of the
approximated posterior pdf is computed as $\hat{X}_{t} = \sum_{p=1}^{P}w_{p_{t}} X_{t}.$
The particles are assigned equal weight ($w_{p_{t}}=1/P$) after the importance
re-sampling step in approximating the posterior pdf. It should be
emphasized that we skip importance re-sampling step in the scale
filter operation as the scale filter contains \textit{target-only}
area and focuses on scale estimation. Additionally, it is
more likely to get noisy confidence map from $R_{s}$. Finally, at
every iteration we check the variance in the velocity components of
the particles to re-assign velocities from uniform initial
distribution to keep variance high enough.
